Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-15 main.tex
Added missing name in acknowledgmeents

We warmly thank all the children, teachers and staff of the International School
of Geneva, the Institut Florimont and the Haut-Lac school for their
participation and support. We express our great gratitude to Anne Gossin and [TBD] for
inviting us to their surgery, for their involvement in the experiments and for
bearing with our disruptive robots. And finally, we want to say a very special \emph{Thank
you!} to Vincent, Thomas, Valérie, Émilien, Mathieu, Johan, Nicolas, Antoine,
Adèle and Marie: by spending several hours being patient teachers for our
robots, you have paved the way for what may become tomorrow a new way of
learning how to deal with all these letters and words!

>>>>

We warmly thank all the children, teachers and staff of the International School
of Geneva, the Institut Florimont and the Haut-Lac school for their
participation and support. We express our great gratitude to Anne Gossin and
Fanny Lebel for inviting us to their surgery, for their involvement in the
experiments and for bearing with our disruptive robots. And finally, we want to
say a very special \emph{Thank you!} to Vincent, Thomas, Valérie, Émilien,
Mathieu, Johan, Nicolas, Antoine, Adèle and Marie: by spending several hours
being patient teachers for our robots, you have paved the way for what may
become tomorrow a new way of learning how to deal with all these letters and
words!
